---
title: "**Data Mining with Wine Reviews**"
author: "Wesley Stanis"
#runtime: shiny
output:
  html_document:  
  #keep_md: true
  #flexdashboard::flex_dashboard:
    keep_md: true
    orientation: columns
    vertical_layout: fill
---

```{r setup, include=FALSE}
library(flexdashboard)
library(shiny)
#```{r setup, include=FALSE}
#knitr::opts_chunk$set(echo = TRUE)
#```

```



```{r include=FALSE}
library(tidyr)
library(rpart)
library(rattle)
library(rpart.plot)
library(RColorBrewer)
library(Cairo)
require(ggvis)
require(caret)
require(dplyr)
require(wordcloud2)
require(ggplot2)
library("tm")
library("wordcloud")
library("stringr")
library("slam")
library("quanteda")
library("SnowballC")
library("arules")
library(arules)
library("factoextra")
require(rpart)
require(rpart.plot)
require(e1071)
require(kernlab)
require(randomForest)
library(shiny)

```

```{r echo=FALSE}
setwd("C:\\Users...Datasets") #put your path here
df <- read.csv("winemag.csv")
df <- tbl_df(df)
#str(df)
```

**Exploring the Data**
=====================================================================



### Countries
```{r echo=FALSE}
countries <- df %>%
  group_by(country) %>%
  count()

countries <- countries[order(countries$n, decreasing = TRUE),]


ggplot(countries, aes(reorder(country,n),n)) +
  geom_bar(stat = "identity", col="Blue")  + 
  labs(title = "Countries", 
       y = "Reviews", x = "Country") +
  theme(axis.text.x=element_text(angle =90))

```



### Price
```{r echo=FALSE}

summary(df$price)
max(df$price, na.rm = TRUE)
which.max(df$price)
#Max price for wine
df[80291,]

ppc <- data.frame("country" = df$country, 
                  "points" = df$points)
ppc1 <- data.frame("country" = df$country, 
                  "points" = df$points,
                  "price" = df$price)

ppcc <- data.frame(tapply(ppc$points, ppc$country, FUN=sum))
ppcc$country <- row.names(ppcc)
colnames(ppcc) <- c("total_points", "country")

#ggplot(ppcc, aes(x=reorder(total_points), y=country)) + geom_point() +
 # coord_cartesian(xlim = c(0, 2000000))

```


### Total Points by Country
```{r echo=FALSE}
ggplot(ppcc, aes(x=country, y=total_points)) + geom_bar(stat = "identity", col="Blue")+
  theme(axis.text.x = element_text(angle = 90))

```

### Histogram of Points and Top Rated Country by Average Points
```{r echo=FALSE}
pointshist <- ggplot(df, aes(x=points)) + geom_histogram(binwidth = 1, color= 'blue') + 
  coord_cartesian(xlim = c(70, 100))+
  labs(title ="Total Points", x = "Points", y = "Reviews") 
pointshist

top <- ppc %>% group_by(country) %>%
  summarise(AveragePoints = mean(points))
top <- top %>% arrange(desc(AveragePoints))
head(top, n=9)
```



### Price vs Points
```{r echo=FALSE}
df %>%
  
  ggplot(aes(x=df$points, y=df$price))+
  geom_point(alpha=0.3) +
  geom_smooth(method = lm) +
  geom_count() +
  theme_light()
```



### Top Rated Countries
```{r echo=FALSE}
ggplot(top, aes(reorder(x=country, -AveragePoints), y=AveragePoints)) + geom_bar(stat = 'identity') +
  coord_cartesian(ylim = c(80, 95)) +
  theme(axis.text.x = element_text(angle = 90))

```


**Association Rules Mining**
==================================================================


```{r echo=FALSE}
tdf <- data.frame("country" = df$country, 
                  "points" = df$points,
                  "price" = df$price,
                  "province" = df$province,
                  "region" = df$region_1,
                  "variety" = df$variety,
                  "winery" = df$winery)
ntdf <- data.frame("country" = df$country, 
                   "points" = df$points,
                   "price" = df$price,
                   "variety" = df$variety)
tdf$region <- NULL
tdf$winery <- NULL
min_points <- min(tdf$points)
max_points <- max(tdf$points)
bins = 5 
width=(max_points - min_points)/bins;
tdf$points = cut(tdf$points, breaks=seq(min_points, max_points, width))

tdf$price <- as.numeric(tdf$price)

tdf$price <- cut(tdf$price, breaks = c(0,10,20,30,40,50,60,Inf),
              labels=c("very cheap","cheap","somewhat cheap",
                       "average","somewhat expesive","expesive","very expensive"))


dfrule <- df
dfrule$region_1 <- NULL
dfrule$region_2 <- NULL
dfrule$points <- as.numeric(dfrule$points)

#str(dfrule)
```

### Inspecting the Rules

```{r echo=FALSE}


dfrule$points <- cut(dfrule$points, breaks = c(81,85,90,95,100, Inf),
               labels=c("poor rating","slightly below average","slightly above average",
                        "above average","perfect ratings"))

myRules = apriori(dfrule, parameter = list(supp = 0.003, conf = 0.9, maxlen = 5))

rules<-apriori(data=dfrule, parameter=list(supp=0.0001,conf = 0.5), 
               appearance = list(default="lhs",rhs="points=perfect ratings"),
               control = list(verbose=F))
rules2<-apriori(data=tdf, parameter=list(supp=0.0001,conf = 0.8, maxlen = 4), 
               appearance = list(default="lhs",rhs="price=very expensive"),
               control = list(verbose=F))
```



```{r}

inspect(rules2[1:5])
inspect(myRules[1:10])
```



**Support Vector Machine**
==========================================================


### Splitting the Data
```{r echo=FALSE}
ntdf1 <- ntdf %>%
  filter(points > 94)
x <- sample(nrow(ntdf1), nrow(ntdf1) * 2/3)
xtrain <- ntdf1[x, ]
xtest <- ntdf1[-x, ]
xtest <- xtest %>% drop_na(country)


ntdf2 <- na.omit(ntdf1)
ntdf2$variety <- as.character(ntdf2$variety)
set.seed(100)
train <- sample(nrow(ntdf2), 0.7*nrow(ntdf2), replace=FALSE)
TrainSet <- ntdf2[train,]
ValidSet <- ntdf2[-train,]
head(TrainSet)
```


### SVM Model and Predictions

```{r}
svmt1 <- svm(country ~ ., data = xtrain, type = 'C', kernel = 'linear', 
             cross = 3, probability = TRUE)
summary(svmt1)

svmpr <- predict(svmt1, xtest, type = 'prob')
svmpr <- as.data.frame(svmpr)
colnames(svmpr) <- 'predictions'
summary(svmpr)
```



### SVM Predictions
```{r echo=FALSE}
ggplot(svmpr, aes(x=predictions)) + geom_bar(col=I('black'), fill=I('blue'))

```


### Filtering Data to Wines over 87 Points
```{r echo=FALSE}


###filtering again but for wines rated above average.
df_no_desc <- df
df_no_desc <- na.omit(df_no_desc)
df_no_desc$description <- NULL
df_no_desc$above_87 <- as.factor(df_no_desc$points > 87)
```


```{r}
#new split of the data
x2 <- sample(nrow(df_no_desc), nrow(df_no_desc) * 2/3)
x2train <- df_no_desc[x, ]
x2test <- df_no_desc[-x, ]
```

### SVM for Wines Rated Above Average

```{r echo=FALSE}
#another support vector Machine model for above average wines
svm_p <- svm(above_87 ~ country + price + variety, data = x2train, 
             type = 'C', kernel = 'linear', 
             cross = 3, probability = TRUE)
summary(svm_p)
svm_points <- predict(svm_p, x2test, type = 'prob')
svm_points <- as.data.frame(svm_points)
colnames(svm_points) <- 'predictions'
summary(svm_points)
```



-----------------------------------------------------------------------
### Plot of SVM Above Average
```{r echo=FALSE}

#plotting model
ggplot(svm_points, aes(x=predictions)) + geom_bar(col=I('black'), fill=I('blue'))
```


**Decision Tree & Linear Model**
==================================================================




### Decision Tree
```{r}
#decision tree
DecisionTree <- rpart(above_87 ~ country + price + variety, data = x2train, method = 'class', 
                      control = rpart.control(cp = 0, minsplit = 2, maxdepth = 3))
#summary(DecisionTree)
fancyRpartPlot(DecisionTree, cex=.7)
```




### Distribution of Price
```{r echo=FALSE}

###Linear model plus more charts
ggplot(df, aes(x=log(price), col=I('black'), fill=I('blue'))) +geom_histogram()

```

### Linear Model of Points by Price and Country
```{r}
lm1 <- (lm(df$points ~ df$price+df$country))
```

### Model Summary
```{r}
summary(lm1)
```


### Plots of Model
```{r echo=FALSE}

plot(lm1)
lm2 <- (lm(df$points ~ df$price))
#summary(lm2)
```

**Naive Bayes**
===============================================================

### Naive Bayes
```{r echo=FALSE}
#Naive Bayes model
nb1 <- naiveBayes(as.factor(country) ~ ., data = xtrain)
summary(nb1)
nbpred1 <- predict(nb1, xtrain, type = 'class')

summary(nbpred1)

nb2 <- predict(nb1, xtest, type = 'class')
nb2 <- data.frame(nb2)
colnames(nb2)[1] <- 'country'
nb2$row <- 1:nrow(nb2)
nb2 <- nb2 %>% select(row, country)
head(nb2, n = 20)
#table(nb2)


```

### Naive Bayes for Average Points of Above 87
```{r echo=FALSE}
nb_p <- naiveBayes(as.factor(above_87) ~ ., data = x2train)
summary(nb_p)
nb_pr <- predict(nb_p, x2train, type = 'class')


nb_p2 <- predict(nb_p, x2test, type = 'class')
summary(nb_p2)
nb_p2 <- data.frame(nb_p2)
colnames(nb_p2)[1] <- 'above_87'
nb2$row <- 1:nrow(nb2)
nb2 <- nb2 %>% select(row, country)
head(nb2, n = 20)
#table(nb2)

nbTrain <- naiveBayes(as.factor(above_87) ~ ., data = x2train)
nbTrainPred <- predict(nbTrain, x2train, type = 'class')

```

**Review Text**
============================================================
```{r}
clean_corpus<-function(text){
  text_corpus<-Corpus(VectorSource(text),readerControl=list(language="english"))%>%
    tm_map(stripWhitespace)%>%
    tm_map(tolower)%>%
    tm_map(removeWords,c(stopwords("english"),"wine"))%>%
    tm_map(stemDocument)
  return(text_corpus)
}

```

```{r echo=FALSE}
corpus<-clean_corpus(df$description)
```



```{r echo=FALSE}
dtm<-DocumentTermMatrix(corpus)
term_freq<-findFreqTerms(dtm,1200)
dtm<-TermDocumentMatrix(corpus,control=
                          list(dictionary=term_freq,removeNumbers=TRUE,
                               stopwords=TRUE,
                               weighting=weightTfIdf))


dtm_matrix<-as.matrix(dtm)
term_freq1<-rowSums(dtm_matrix)[order(rowSums(dtm_matrix), 
                                      decreasing = TRUE)]


```




### Wordcloud
```{r}

wordfreq<-data.frame(word=names(term_freq1),freq=term_freq1)
wordcloud2(wordfreq)

```



















